### 2021-09-08 paper/localpsf.tex
wrote poincare-like result proof

\begin{lem}[Preparation for Theorem \ref{thm:smoothest_interpolant}]
	\label{lem:T_is_linear}
	Let $\Omega \subset \mathbb{R}^d$, $d\in\{1,2,3\}$, be an open bounded domain with a bounded extension operator, let $x_i \in \Omega$ for $i=1,\dots,r$, and let $f \in \mathbb{R}^r$. Consider the optimization problem
	\begin{equation}
	\label{eq:generic_optimization_initial}
	\begin{aligned}
	\min_{\gamma \in H^2_N(\Omega)} &\quad \frac{1}{2}\norm{\Delta \gamma}_{L^2(\Omega)}^2 \\
	\text{such that} &\quad \gamma(x_i) = f_i, \quad i=1,\dots,r.
	\end{aligned}
	\end{equation}
	A minimizer, $\gamma^*$, of \eqref{eq:generic_optimization_initial} is a function defined on $\Omega$ that interpolates the data pairs $(x_i,f_i)$, and is as flat as possible in a least squares sense.
	The following statements hold.
	\begin{enumerate}
		\item[(a)] There exists a unique solution to \eqref{eq:generic_optimization_initial}.
		\item[(b)] 	Let $\mathcal{T}:\mathbb{R}^r \rightarrow H^2(\Omega)$ denote the solution operator for optimization problem \eqref{eq:generic_optimization_initial}	as a function of $f$. That is, 
		\begin{equation}
		\label{eq:opt_soln_operator}
		\mathcal{T}(f) := \gamma^*,
		\end{equation}
		where $\gamma^*$ is the minimizer of \eqref{eq:generic_optimization_initial}. The operator $\mathcal{T}$ is a linear operator.
	\end{enumerate}
\end{lem}
\begin{proof}
	By the Sobolev Imbedding Theorem (see, e.g., Theorem 7.20 in \cite{ARBOGAST}), $H^2_N(\Omega)$ is continuously imbedded in $C^0(\Omega)$, so pointwise evaluation $u \mapsto u(x_i)$ of functions at a point $x_i \in \Omega$ is a continuous linear functional on $H^2_N$. The set 
	\begin{equation}
	\label{eq:inverse_image_of_point}
	\{u \in H^2_N : u(x_i)=f_i\}
	\end{equation}
	is therefore a closed affine set in $H^2_N$, because it is the inverse image of a point under a continuous linear functional. Hence the feasible set for optimization problem \eqref{eq:generic_optimization_initial},
	\begin{equation}
	\label{eq:wi_feasible_set}
	X := \{u \in H^2_N : u(x_i)=f_i~\text{for}~ i=1,\dots,r\},
	\end{equation}
	is a closed affine set in $H^2_N$, because it is the intersection of the sets in \eqref{eq:inverse_image_of_point} for $i=1,\dots,r$. The feasible set $X$ is convex because it is affine, and it is non-empty because interpolating the data pairs $\{(x_i, f_i)\}_{i=1}^r$ using any smooth interpolation method yields an element of $X$. The objective function, $\gamma \mapsto \frac{1}{2}||\Delta \gamma||^2$, is convex because it

	We now show that the objective function is strongly convex on the tangent space to $X$,
	\begin{equation*}
	X_0 := \{u \in H^2_N : u(x_i)=0~\text{for}~ i=1,\dots,r\}.
	\end{equation*}

>>>>

\begin{defn}[Weighting function optimization problem]
	Let $\Omega \subset \mathbb{R}^d$, $d\in\{1,2,3\}$, be an open bounded domain with, let $x_i \in \Omega$ for $i=1,\dots,r$, and let $f \in \mathbb{R}^r$. We consider the optimization problem
	\begin{equation}
	\label{eq:generic_optimization_initial}
	\begin{aligned}
	\min_{\gamma \in H^2_N(\Omega)} &\quad \frac{1}{2}\norm{\Delta \gamma}_{L^2(\Omega)}^2 \\
	\text{such that} &\quad \gamma(x_i) = f_i, \quad i=1,\dots,r.
	\end{aligned}
	\end{equation}
	A minimizer, $\gamma^*$, of \eqref{eq:generic_optimization_initial} is a function defined on $\Omega$ that interpolates the data pairs $(x_i,f_i)$, and is as flat as possible in a least squares sense. 
	We denote the objective function for optimization problem \eqref{eq:generic_optimization_initial} by 
	\begin{equation}
	\label{eq:wi_objective}
	J(\gamma) := \frac{1}{2}||\Delta \gamma||^2_{L^2(\Omega)}.
	\end{equation}
	We denote the feasible set for optimization problem \eqref{eq:generic_optimization_initial} by 
	\begin{equation}
	\label{eq:wi_feasible_set}
		X := \{u \in H^2_N : u(x_i)=f_i~\text{for}~ i=1,\dots,r\}.
	\end{equation}
	We denote the tangent space to the feasible set by
	\begin{equation}
	\label{eq:wi_tangent_space}
	X_0 := \{u \in H^2_N : u(x_i)=0~\text{for}~ i=1,\dots,r\}.
	\end{equation}
\end{defn}

\begin{lem}[Elliptic regularity on $X_0$]
	\label{lem:elliptic_regularity_x0}
	If $\partial \Omega$ is $C^{1,1}$, then there exists a constant $C > 0$ such that
	\begin{equation*}
		||u||_{H^2(\Omega)} \le C ||\Delta u||_{L^2(\Omega)}
	\end{equation*}
	for all $u \in X_0$.
\end{lem}

\begin{proof}
	Let $\widetilde{u}$ be version of $u$ that has been shifted up or down by a constant such that $\int_\Omega \overline{u} = 0$. We have
	\begin{align*}
		||D^1 u||_{\left(L^2(\Omega)\right)^d}^2 + ||D^2 u||_{\left(L^2(\Omega)\right)^{d \times d}}^2 &= ||D^1 \widetilde{u}||_{\left(L^2(\Omega)\right)^d}^2 + ||D^2 \widetilde{u}||_{\left(L^2(\Omega)\right)^{d \times d}}^2\\
		&\le ||\widetilde{u}||_{H^2(\Omega)}^2 \\
		&\le C_1 ||\Delta \widetilde{u}||_{L^2(\Omega)}^2 \\
		&= C_1 ||\Delta u||_{L^2(\Omega)}^2
	\end{align*}
	for some constant $C_1$. In the first and fourth lines we used the fact that the derivative of a constant is zero, in the second line we used the definition of the $H^2$ norm, and in the third line we used the standard elliptic regularity result for pure Neumann problems (see, e.g., Theorem 8.13 (b) in \cite{Arbogast}).

	To complete the proof, we will now show that there exists a constant $C_2$ such that $||u||_{L^2(\Omega)}^2 \le C_2 ||\Delta u||_{L^2(\Omega)}^2$ for all $u \in X_0$. For this, we use a standard compactness argument, which closely follows the proof of Theorem 8.12 in \cite{ARBOGAST}. Suppose for the sake of contradiction that this result does not hold. Then there exists a sequence $\{u_k\}_{k=1}^\infty \subset X_0$ such that
	$||u_k||_{L^2(\Omega)}=1$ and $||\Delta u_k||_{L^2(\Omega)} \le 1/k$.
	By the result already proven, the sequence $u_k$ is bounded in $H^2(\Omega)$ as follows:
	\begin{align*}
	||u_k||_{H^2(\Omega)}^2 &= ||u_k||_{L^2(\Omega)}^2 + ||D^1 u||_{\left(L^2(\Omega)\right)^d}^2 + ||D^2 u||_{\left(L^2(\Omega)\right)^{d \times d}}^2 \\
	&\le ||u_k||_{L^2(\Omega)}^2 + C_1 ||\Delta u||_{L^2(\Omega)}^2 \le 1 + C_1.
	\end{align*}
	Therefore, by the Banach-Alaoglu theorem, there exists a subsequence $u_{k_j}$ and function $u \in X_0$ such that
	\begin{equation*}
		u_{k_j} \overset{w}{\rightharpoonup} u \quad \text{weakly in }H^2(\Omega).
	\end{equation*}
	Let $f \in L^2(\Omega)$. By the Cauchy-Schwarz inequality, the linear functional $v \mapsto \int_\Omega f(x) \Delta v(x) dx$ is bounded in $H^2(\Omega)$, and is therefore an element of $\left(H^2(\Omega)\right)^*$. Weak convergence therefore implies
	\begin{equation*}
		\int_\Omega f(x) \Delta u_k(x) dx \rightarrow \int_\Omega f(x) \Delta u(x) dx.
	\end{equation*}
	By the assumption $||\Delta u_k||_{L^2(\Omega)} \le 1/k$ and Cauchy-Schwarz, we also have 
	\begin{equation*}
	\int_\Omega f(x) \Delta u_k(x) dx \rightarrow 0,
	\end{equation*}
	so we must have
	\begin{equation*}
		\int_\Omega f(x) \Delta u(x) dx = 0.
	\end{equation*}
	Since this holds for all $f \in L^2(\Omega)$, by the fundamental lemma of the calculus of variations, $\Delta u(x) = 0$ almost everywhere in $\Omega$. This, combined with the fact that $u$ has Neumann zero boundary conditions, implies that $u$ is a constant function. Since $u$ has value zero at least one point in each connected component of $\Omega$, we have $u=0$. Note that pointwise values of $u$ are well-defined since the Sobolev embedding theorem imples that $H^2(\Omega)$ is continuously imbedded in the space of continuous functions $C^0(\Omega)$ when $d < 4$, and we are considering $d \in \{1,2,3\}$ (see, e.g., Theorem 7.19 in \cite{Arbogast}).

	On the other hand, by the Rellich-Kondrachov theorem, $H^2(\Omega)$ is compactly imbedded in $L^2(\Omega)$, so there must exist a sub-sub-sequence, $u_{k_{j_i}}$ such that 
	\begin{equation*}
		u_{k_{j_i}} \rightarrow u
	\end{equation*}
	strongly in $L^2(\Omega)$. By assumption $||u_{k_{j_i}}||_{L^2(\Omega)}=1$, so $||u||_{L^2(\Omega)}=1$. This contradicts the result $u=0$ that we previously derived, so we must conclude that there exists a constant $C_2 > 0$ such that
	\begin{equation*}
		||u||_{L^2(\Omega)} \le C_2 ||\Delta u||_{L^2(\Omega)}.
	\end{equation*}
	for all $u \in X_0$. Combining this with out previous result, we have
	\begin{equation*}
	||u||^2_{H^2(\Omega)} \le (C_1 + C_2)||\Delta u||^2
	\end{equation*}
	for all $u \in X_0$, which completes the proof.
\end{proof}

\begin{lem}[Well-posedness of weighting function optimization problem]
	\label{lem:wi_existence_and_uniqueness}
	There exists a unique solution to optimization problem \eqref{eq:generic_optimization_initial}.
\end{lem}

\begin{proof}
	By the Sobolev Imbedding Theorem (see, e.g., Theorem 7.20 in \cite{ARBOGAST}), $H^2_N(\Omega)$ is continuously imbedded in $C^0(\Omega)$, so pointwise evaluation $u \mapsto u(x_i)$ of functions at a point $x_i \in \Omega$ is a continuous linear functional on $H^2_N$. The set 
	\begin{equation}
	\label{eq:inverse_image_of_point}
	\{u \in H^2_N : u(x_i)=f_i\}
	\end{equation}
	is therefore a closed affine set in $H^2_N$, because it is the inverse image of a point under a continuous linear functional. Hence the feasible set $X$, defined in \eqref{eq:wi_feasible_set}, is a closed affine set in $H^2_N$, because it is the intersection of the sets in \eqref{eq:inverse_image_of_point} for $i=1,\dots,r$.

	The feasible set $X$ is convex because it is affine, and it is non-empty because interpolating the data pairs $\{(x_i, f_i)\}_{i=1}^r$ using any smooth interpolation method yields an element of $X$. Furthermore, the objective function, 
	\begin{equation}
	J(\gamma) := \frac{1}{2}||\Delta \gamma||^2_{L^2(\Omega)},
	\end{equation}
	is convex because it is the composition of a convex function with a linear map. Furthermore, the elliptic regularity result in Lemma \ref{lem:elliptic_regularity_x0} implies
	\begin{equation*}
		J''(\gamma)v^2 = ||\Delta v||^2_{L^2(\Omega)} \ge C ||v||_{H^2(\Omega)}^2
	\end{equation*}
	for all $v \in X_0$, which implies that $J$ is strongly convex on $X$.
\end{proof}

\begin{lem}[Linearity of weighting function solution operator]
	\label{lem:T_is_linear}
	Let $\mathcal{T}:\mathbb{R}^r \rightarrow H^2(\Omega)$ denote the solution operator for optimization problem \eqref{eq:generic_optimization_initial}	as a function of $f$. That is, 
		\begin{equation}
		\label{eq:opt_soln_operator}
		\mathcal{T}(f) := \gamma^*,
		\end{equation}
		where $\gamma^*$ is the minimizer of \eqref{eq:generic_optimization_initial}. The operator $\mathcal{T}$ is a linear operator.
\end{lem}

\begin{proof}
	asdf
\end{proof}
